\textit{Supporting Information for}: How is experience transformed into memory?

### 2019-04-17 paper/main.tex
added wasserstein figure and text, did not compile the pdfs bc i dont have latex on this computer

\newcommand{\topicopt}{S1}
\newcommand{\topics}{S2}
\newcommand{\featureimportance}{S3}
\newcommand{\listlearning}{S4}
\newcommand{\corrmats}{S5}
\newcommand{\matchmats}{S6}

@@

>>>>

\newcommand{\topicopt}{S1}
\newcommand{\topics}{S2}
\newcommand{\featureimportance}{S3}
\newcommand{\listlearning}{S4}
\newcommand{\corrmats}{S5}
\newcommand{\matchmats}{S6}
\newcommand{\wasserstein}{S7}

@@

We also evaluated a parameter-free procedure for choosing $K$, which finds the $K$ value that maximizes the Wasserstein distance (a.k.a. "Earth mover's" distance) between the within and across event distributions of correlation values. This alternative procedure largely replicated the pattern of results found with the parameterized method described above, but recovered substantially fewer events on average (Fig.\wasserstein). While both approaches seem to underestimate the number of video/recall events relative to the "true" number (as determined by human raters), the parameterized approach was closer to the true number.

### 2019-04-17 paper/supporting_information.tex
minor edits needed for nature submission
added wasserstein figure and text, did not compile the pdfs bc i dont have latex on this computer

\section*{Overview}
This document provides additional details about the methods we used in the main text.  We also include some additional analyses and figures referenced in the main text.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/parameter_search}
\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over video sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$, and number of topics ($K \in \{5, 10, 25, 50, 100 \}$.  The reported correlations are between per-subject video-recall trajectory correlations and per-subject hand-annotated memory performance ratings.}
\label{fig:paramsearch}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.75\textwidth]{figs/topic_words}
\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.  We identified 27 unique topics with non-zero weights (we used $K=100$ topics to fit the model).  Each topic comprises a distribution of weights over all words in the vocabulary.  For each topic, we show the words with the 10 largest weights, along with a suggested description of the topic.}
\label{fig:topics}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1\textwidth]{figs/feature_value}
\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the video trajectory. The bar heights reflect the correlation between the video trajectory computed using all features with a video trajectory computed using all features except the indicated feature.  (Lower bars reflect features that contribute more substantially to the video trajectory's shape.) \textbf{B.} Which features are preserved during recall?  The bar heights reflect the (average) across-participant correlations between the video and recall trajectories.  Error bars denote bootstrap-estimated standard error of the mean.  \textbf{C.} Feature correlation matrix.  Each entry displays the correlation between video topic trajectories created using only the indicated (row/column) features.}
\label{fig:feature-importance}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1\textwidth]{figs/list_learning}
\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video. \textbf{B}.  The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the video.  \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.  All panels: error bars denote bootstrap-estimated standard error of the mean.}
\label{fig:list-learning}
\end{figure}

@@

\section*{Participant-level figures referenced in the main text}

@@

\begin{figure}[htp]
\centering
\includegraphics[width=\textwidth]{figs/corrmats}
\caption{\small \textbf{Recall trajectory temporal correlation matrices and event segmentation fits.} Each panel is in the same format as Figure~2E in the main text.  The yellow boxes indicate HMM-identified event boundaries.}
\label{fig:corrmats}
\end{figure}

\begin{figure}[htp]
\centering
\includegraphics[width=\textwidth]{figs/matchmats}
\caption{\small \textbf{Video-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.  The yellow boxes mark the maximum correlation in each column.}
\label{fig:matchmats}
\end{figure}

>>>>

\section*{Overview}
This document provides additional details about the methods we used in the main text.  We also include some additional analyses referenced in the main text.

@@

\begin{figure}[p!]
\centering
\includegraphics[width=1\textwidth]{figs/parameter_search}
\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over video sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$, and number of topics ($K \in \{5, 10, 25, 50, 100 \}$.  The reported correlations are between per-subject video-recall trajectory correlations and per-subject hand-annotated memory performance ratings.}
\label{fig:paramsearch}
\end{figure}

@@

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/topic_words}
\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.  We identified 27 unique topics with non-zero weights (we used $K=100$ topics to fit the model).  Each topic comprises a distribution of weights over all words in the vocabulary.  For each topic, we show the words with the 10 largest weights, along with a suggested description of the topic.}
\label{fig:topics}
\end{figure}

@@

\begin{figure}[p!]
\centering
\includegraphics[width=1\textwidth]{figs/feature_value}
\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the video trajectory. The bar heights reflect the correlation between the video trajectory computed using all features with a video trajectory computed using all features except the indicated feature.  (Lower bars reflect features that contribute more substantially to the video trajectory's shape.) \textbf{B.} Which features are preserved during recall?  The bar heights reflect the (average) across-participant correlations between the video and recall trajectories.  Error bars denote bootstrap-estimated standard error of the mean.  \textbf{C.} Feature correlation matrix.  Each entry displays the correlation between video topic trajectories created using only the indicated (row/column) features.}
\label{fig:feature-importance}
\end{figure}

@@

\begin{figure}[p!]
\centering
\includegraphics[width=1\textwidth]{figs/list_learning}
\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video. \textbf{B}.  The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the video.  \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.  All panels: error bars denote bootstrap-estimated standard error of the mean.}
\label{fig:list-learning}
\end{figure}

@@

%\section*{Participant-level figures referenced in the main text}

@@

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/corrmats}
\caption{\small \textbf{Recall trajectory temporal correlation matrices and event segmentation fits.} Each panel is in the same format as Figure~2E in the main text.  The yellow boxes indicate HMM-identified event boundaries.}
\label{fig:corrmats}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/matchmats}
\caption{\small \textbf{Video-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.  The yellow boxes mark the maximum correlation in each column.}
\label{fig:matchmats}
\end{figure}

\begin{figure}[p!]
  \centering
  \includegraphics[width=\textwidth]{figs/trajectory_wasserstein}
  \caption{\small \textbf{Trajectories using Wasserstein distance for choosing $K$.}  We replicated the trajectory analysis using Wasserstein distance, a parameter-free procedure for choosing $K$. Overall, the pattern of findings is quite similar to our main approach, but resulted in a smaller number of events.}
  \label{fig:trajectory_wasserstein}
  \end{figure}
